R Notebook

### 2019-09-03 src/testing_file.Rmd
rastervis testing

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0.1, 1, 0.1) #for legend
redtrans <- rgb(218, 215, 216, 90, maxColorValue=255) 
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

#for (pred in 1:length(maplst)){
  pras5 <- raster(maplst[33])
  pras180 <- raster(maplst[14])
  pras370 <- raster(maplst[28])
  pras697 <- raster(maplst[41])
  crs(pras5) <- apr
  crs(pras180) <- apr
  crs(pras370) <- apr
  crs(pras697) <- apr
  ascname5 <- names(pras5)
  ascname180 <- names(pras180)
  ascname370 <- names(pras370)
  ascname697 <- names(pras697)

par(mfrow=c(1,2))

  #pras[pras >0] <- 1
  lp5 <- plot(pras5, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  #lp <- plot(pras5)
  lp5 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp5 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  l180 <- plot(pras180, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  #lp <- plot(pras5)
  lp180 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp180 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  print(lp5)
  dev.copy(png, (paste0("../output/maxent/all_data/predictions/", ascname5, pred, ".png")), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
#}

  print(lp5)
  dev.copy(png, (paste0("../output/maxent/all_data/predictions/", ascname5, pred, ".png")), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
#}

@@

>>>>

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
redtrans <- rgb(218, 215, 216, 120, maxColorValue=255) #mcp
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

  pras6 <- raster(maplst[37])
  pras180 <- raster(maplst[14])
  pras370 <- raster(maplst[28])
  pras697 <- raster(maplst[41])
  crs(pras6) <- apr
  crs(pras180) <- apr
  crs(pras370) <- apr
  crs(pras697) <- apr
  ascname6 <- names(pras6)
  ascname180 <- names(pras180)
  ascname370 <- names(pras370)
  ascname697 <- names(pras697)

par(mfrow=c(1,4))

  lp6 <- plot(pras6, breaks=brk,  col=rev(lgc), axes = FALSE, box = FALSE, legend = FALSE)
  lp6 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp6 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  lp180 <- plot(pras180, breaks=brk,  col=rev(lgc), axes = FALSE, box = FALSE, legend = FALSE)
  lp180 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp180 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  lp370 <- plot(pras370, breaks=brk,  col=rev(lgc), axes = FALSE, box = FALSE, legend = FALSE)
  lp370 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp370 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  lp697 <- plot(pras697, breaks=brk,  col=rev(lgc), axes = FALSE, box = FALSE, legend = TRUE)
  lp697 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp697 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  print(lp6)
  dev.copy(png, (paste0("../output/maxent/all_data/predictions/testplots/", ascname6, ".png")), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
#}

  print(lp5)
  dev.copy(png, (paste0("../output/maxent/all_data/predictions/", ascname5, ".png")), width = 1920,height = 1080)
  dev.off() # stops automatic saving of the plot to a png))
#}

@@

as above but with rcolorbrewer
```{r}
lp6 <- plot(pras6, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  lp6 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp6 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  lp180 <- plot(pras180, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  lp180 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp180 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  lp370 <- plot(pras370, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  lp370 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp370 <- plot(s, col = "#474646", border = "#474646", add = TRUE)

  lp697 <- plot(pras697, breaks=brk, col=rev(colorRampPalette(brewer.pal(10, "Spectral"))(10)), axes = FALSE, box = FALSE, legend = TRUE)
  lp697 <- plot(outsidemcp,  col = redtrans, border = redtrans, add = TRUE)
  lp697 <- plot(s, col = "#474646", border = "#474646", add = TRUE)
```

with rastervis

```{r}
aea <- raster("../output/env/aea.tif") #the correct CRS
maplst <- list.files("../output/maxent/predictions/may", pattern = "^avg_clog.*.asc", full.names = TRUE)
s <- shapefile("../data/env/landp/landpro.shp") #made in arcgis
apr <- aea@crs
brk <- seq(0, 1, 0.1) #for legend
lgc <- sequential_hcl(10, palette = "YlOrRd") #colour scheme from colorspace package
redtrans <- rgb(218, 215, 216, 120, maxColorValue=255) #mcp
outsidemcp <- shapefile("../data/env/landp/mcpout.shp") #made in arcgis

pras6 <- raster(maplst[37])
pras180 <- raster(maplst[14])
pras370 <- raster(maplst[28])
pras697 <- raster(maplst[41])
crs(pras6) <- apr
crs(pras180) <- apr
crs(pras370) <- apr
crs(pras697) <- apr
ascname6 <- names(pras6)
ascname180 <- names(pras180)
ascname370 <- names(pras370)
ascname697 <- names(pras697)
pstack <- stack(pras6, pras180, pras370, pras697) #stack the layers

pras1 <- raster(maplst[1])
pras2 <- raster(maplst[2])
pras3 <- raster(maplst[3])
pras4 <- raster(maplst[4])
crs(pras1) <- apr
crs(pras2) <- apr
crs(pras3) <- apr
crs(pras4) <- apr

pstack <- stack(pras6, pras180, pras370, pras697, pras1, pras2, pras3, pras4) #stack the layers

cls <- c("6m", "180m", "370m", "697m")
rws <- c("may", "dummy")
mapTheme <- rasterTheme(region = rev(brewer.pal(10,"RdYlGn")))
my.at <- seq(0, 1, by = 0.1)

p <- levelplot(pstack, ylab = NULL, xlab = NULL, scales=list(draw=FALSE), colorkey=list(space="bottom", at = my.at), par.settings = mapTheme, layout = c(4, 2), names.attr = c("6m", "180m", "370m", "697m", "", "", "", ""))
p + layer(sp.polygons(s, fill = "black")) + layer (sp.polygons(outsidemcp, fill = redtrans, col = NA))

png("../output/maxent/predictions/testplots/rasterVis.png", height = 1024 * 0.707, width = 1024)
p
dev.off()
